%-------------------------
% CV - Hoàng Tấn Đạt
%-------------------------
\documentclass[a4paper,11pt]{article}

% Font & encoding
\usepackage[utf8]{vietnam}
\usepackage[T5]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

% Margins
\usepackage[top=0.9cm, bottom=0.9cm, left=1.3cm, right=1.3cm]{geometry}

% Sections
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{2pt}

% Lists
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.3em, itemsep=0pt, topsep=1pt, parsep=0pt}

% Remove paragraph indent
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.28em}

% Two-line entry: {bold left}{right} / {italic left}{italic right}
\newcommand{\entry}[4]{%
    \noindent\textbf{#1} \hfill #2 \\
    \noindent\textit{#3} \hfill \textit{#4}\par
}

\begin{document}

% ========== HEADER ==========
\begin{center}
    {\Huge \textbf{Hoàng Tấn Đạt}} \\[6pt]
    Ho Chi Minh City, Viet Nam \ | \
    \href{mailto:datdat2kk5@gmail.com}{datdat2kk5@gmail.com} \ | \
    (+84) 799 165 330 \\[2pt]
    \href{https://linkedin.com/in/dathoang1412}{linkedin.com/in/dathoang1412} \ | \
    \href{https://github.com/dathoang1412}{github.com/dathoang1412}
\end{center}

% ========== SUMMARY ==========
\section{Summary}
Software engineering student focused on \textbf{frontend development with React.js and Next.js}, with full-stack experience across Node.js, real-time systems, and AI integration. Comfortable working in English and at a fundamental Japanese level.

% ========== EXPERIENCE ==========
\section{Experience}

\entry{FPT Software (FSoft)}{Jul 2025 -- Oct 2025}
      {Frontend Developer Intern --- \textbf{Next.js}}{Ho Chi Minh City, Viet Nam}
\begin{itemize}
    \item Developed frontend features with \textbf{Next.js} and \textbf{TypeScript} for an enterprise web application delivered to a \textbf{Japanese client}.
    \item Built responsive, spec-compliant UI components and integrated REST APIs with backend and QA teams.
    \item Worked in an agile process with code reviews and Japanese-standard documentation and quality requirements.
\end{itemize}

% ========== PROJECTS ==========
\section{Projects}

\entry{GU.AI --- AI Fashion Photography Platform}{2026 | Team of 3}
      {Full-stack --- \textbf{Next.js}, TypeScript, Node.js, MongoDB, Socket.IO}
      {\href{https://guai.com.vn}{guai.com.vn} $\cdot$ \href{https://github.com/GU-AI-enterprise}{github}}
\begin{itemize}
    \item Built a full-stack SaaS platform (\textbf{Next.js} web app, REST API with \textbf{$\sim$85 endpoints}, and admin panel) with \textbf{9 AI tools} for fashion sellers --- virtual try-on, model generation, and image/video editing, powered by Fashn.ai.
    \item Implemented \textbf{credit-based billing} with PayOS payments, subscription plans, and dynamic per-tool pricing.
    \item Integrated \textbf{Google Gemini} for an in-studio AI assistant with \textbf{RAG-based} template search, plus real-time notifications and support chat using Socket.IO.
    \item Built admin features for live monitoring, \textbf{RBAC} user management, and revenue analytics.
\end{itemize}

\entry{BookHub}{2025 | Team of 5}
      {Full-stack --- \textbf{React.js}, TailwindCSS, Node.js, Express, MongoDB}
      {\href{https://github.com/Bookhub-SWD}{github.com/Bookhub-SWD}}
\begin{itemize}
    \item Built a full-stack platform for book lending and community discussion, supporting borrowing, lending, and user reviews.
    \item Developed the frontend with \textbf{React.js} and TailwindCSS for book search, personal library management, and review creation.
    \item Implemented backend services with Node.js, Express, and MongoDB for book availability, borrowing history, and community activity.
\end{itemize}

% ========== EDUCATION ==========
\section{Education}

\entry{FPT University}{Oct 2023 -- Feb 2027 (Expected)}
      {Bachelor's Degree in Information Technology}{Ho Chi Minh City, Viet Nam}

% ========== SKILLS ==========
\section{Skills}
\noindent
\textbf{Programming Languages:} JavaScript, TypeScript, C/C++, Java \\
\textbf{Frontend:} \textbf{Next.js}, React.js, TailwindCSS \\
\textbf{Backend:} Node.js, Express, REST API, Socket.IO \\
\textbf{Database:} PostgreSQL, MongoDB \\
\textbf{Developer Tools:} Git, Docker, CI/CD \\
\textbf{Foreign Languages:} English, Japanese (Fundamental) \\
\textbf{Interests:} Software Development, AI Integration, High-Performance Systems, Competitive Programming

% ========== AWARDS ==========
\section{Awards \& Achievements}

\entry{ICPC National Contest}{2025}
      {Contestant --- competed with top university programming teams in the region}{}

\end{document}
